Stack Safety as a Security Property

### 2020-07-09 main.tex
Tweaks

\Cref{fig:running-program} shows a high-level view of our running example,
written in C-like pseudo-code.  It consists of a {\tt main} function that
performs a call to some function {\tt f}, which in turns makes a nested call
to some function {\tt g} before returning, while performing some simple
arithmetic operations in the process. \cref{fig:running-trace-b} shows an
execution trace of corresponding machine instructions. (These might have
been generated by compiling the high-level code, but it is only the behavior
of the machine instructions that we care about
here---\Cref{fig:running-program} is our actual running example.)

@@

\begin{figure}
  \integrityexample
  \caption{Failing Trace Integrity}
  \label{fig:intex}
\end{figure}

@@

\paragraph*{A conservative policy}
%
The first micropolicy we present to enforce the definition of stack
safety developed in \cref{sec:lse-and-wbcf} is \leo{a small variation
  of?}  the Depth Isolation policy presented by
\citet{DBLP:conf/sp/RoesslerD18}. Their policy tags the stack memory
with ownership information associated to each stack frame (and to each
separate object inside that frame, a more finely grained access
control that we do not need to consider here), and registers holding
stack pointers with matching access permission information. Beyond
those capabilities, the compiler generates designated sequences of
instructions with special tags that grant them permission to manage
the stack, say during calls and returns. \rb{Conceivably on alloc
  operations, etc., which we have not yet mentioned.}

@@

\paragraph*{Strong Stack Safety}

@@

\section{Discussion}

\rb{Notes from meeting:
  \begin{itemize}
  \item Explain how the theory applies to production compilers like GCC and
    LLVM, which aspects are directly applicable, what are the effects of
    alternative calling conventions. Other less charted waters: tail calls,
    coroutines, jumps into supervisor mode.
  \item CHERI and its operation, documentation and practical configurations and
    operation.
  \item Compare and contrast with StkTokens.
  \item Under what circumstances can stack safety exist without an enforcement
    mechanism?
  \item Zeroing out of allocated space inside blessed sequences, eager vs lazy.
    Possibility of blessed alloc and dealloc sequences, which also manipulate SP
    and would not be legal without blessing. In such an extended setting, the
    return sequence would check for matching addresses (it would be nice to have
    testing for this!).
  \end{itemize}
}

>>>>

\Cref{fig:running-program} shows a high-level view of our running example,
written in C-like pseudo-code.  It consists of a {\tt main} function that
performs a call to some function {\tt f}, which in turns makes a nested call
to some function {\tt g} before returning, while performing some simple
arithmetic operations in the process. \cref{fig:running-trace-b} shows an
execution trace of corresponding machine instructions. (These might have
been generated by compiling the high-level code, but it is only the behavior
of the machine instructions that we care about
here---\Cref{fig:running-trace-b} is our actual running example.)

@@

\begin{figure}
  \integrityexample
  \caption{Failing Trace Integrity\bcp{the ``108'' is not placed right}}
  \label{fig:intex}
\end{figure}

@@

\subsection{A Conservative Policy}
%
The first micropolicy we present to enforce the definition of stack
safety developed in \cref{sec:lse-and-wbcf} is \leo{a small variation
  of?}  the Depth Isolation policy presented by
\citet{DBLP:conf/sp/RoesslerD18}. Their policy tags the stack memory
with ownership information associated to each stack frame (and to each
separate object inside that frame, a more finely grained access
control that we do not need to consider here), and registers holding
stack pointers with matching access permission information. Beyond
those capabilities, the compiler generates designated sequences of
instructions with special tags that grant them permission to manage
the stack, say during calls and returns. \rb{Conceivably on alloc
  operations, etc., which we have not yet mentioned.}

@@

\subsection{A Stronger Stack Safety Property}

@@

% \rb{Notes from meeting:
%   \begin{itemize}
%   \item Explain how the theory applies to production compilers like GCC and
%     LLVM, which aspects are directly applicable, what are the effects of
%     alternative calling conventions. Other less charted waters: tail calls,
%     coroutines, jumps into supervisor mode.
%   \item CHERI and its operation, documentation and practical configurations and
%     operation.
%   \item Compare and contrast with StkTokens.
%   \item Under what circumstances can stack safety exist without an enforcement
%     mechanism?
%   \item Zeroing out of allocated space inside blessed sequences, eager vs lazy.
%     Possibility of blessed alloc and dealloc sequences, which also manipulate SP
%     and would not be legal without blessing. In such an extended setting, the
%     return sequence would check for matching addresses (it would be nice to have
%     testing for this!).
%   \end{itemize}
% }
